Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-18 02_methods/methods.tex
start with the normalization

>>>>

\begin{figure}
  \centering
  \hspace*{\fill}
  \subfigure[Patient 1]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
  \subfigure[Patient 2]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure}

In this work, we proposed a method to normalized \ac{dce}-\ac{mri} prostate data.
However, it can be note that this method can be used for any \ac{dce}-\ac{mri} sequences.
The aim of the method is to reduce the intra-patient variation that can occur during the acquisition.
These variations can be highlighted by observing the evolution of the intensity \ac{pdf} of the \ac{dce}-\ac{mri} over time, as shown in Fig.\,\ref{fig:heatmap}.
These variations are:
(i) an offset of the peak value before pre-contrast,
(ii) a time offset depending of the contrast injection, and
(iii) a scale factor related to the enhancement.
Therefore, our normalization method should attenuate all these variations

\subsubsection{Baseline alignment of each \ac{dce}-\ac{mri} serie}

Short-path using graph minimization.

\subsubsection{Estimate the dispersion of the voxel intensities}

MSE.

\subsubsection{Parametric curve alignment}

Model using 1 translation and one scale.

### 2016-08-18 03_experiments/experiments.tex
start with the normalization

>>>>

\subsection{Implementation}

The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
The data used for this work are also publicly available\footnote{\url{http://some-url.com}}.
